---
title: "GitHub Data Analytics and Visualization"
author: "Gopi Sandeep Guntuku"
date: "3/30/2022"
output: html_document
---
### **GitHub User: Johnny Chivers**

Johnny Chivers is a Full-Time AWS Data Guru and Part-Time YouTuber. 

The details of the Github Repository : Max Johnny Chivers has 33 repositories and 25 followers.
The repositories are based on the tutorials uploaded in youtube.

The Github link : https://github.com/johnny-chivers

### **Code**
##### **Loading the libraries required in the project:**

```{r }
library(gh)
library(httr)
library(tidyverse)
library(kableExtra)
library(ggthemes)
```

Updating the personal token from GitHub

```{r }
# Token from Github
my_github_token = "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"
Sys.setenv(GITHUB_TOKEN = my_github_token)

```

### **Table 1**

Creating a table showing johnny chiver’s login, name, public_repos, followers.

```{r}

johnny_chivers <- gh("GET /users/johnny-chivers", 
                     username = "johnny-chivers",.limit=Inf)

```


Class, Length and Names of the followers are extracted.
```{r}

class(johnny_chivers)

```


```{r}

length(johnny_chivers)

```

```{r }

names(johnny_chivers)

```

DataFrame for getting login, name, puclic_repos, followers.

```{r }

johnny_chivers <- tibble(
  login = johnny_chivers$login,
  name = johnny_chivers$name,
  public_repos = johnny_chivers$public_repos,
  followers = johnny_chivers$followers
)

```

Visualizing the tabular data using Kable

```{r }

head(johnny_chivers, n = 50) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("bordered","condensed","responsive"))

```
### **Table 2**

Creating a table showing johnny chiver follower's login, name, public_repos, followers.


```{r }

# followers list fetching
johnny_followers <- gh("/users/johnny-chivers/followers", .limit = Inf)

# followers dataframe creation
df_johnny_followers <- data.frame(User=character(),
                           login=character(), 
                           public_repos=integer(), 
                           followers=integer())

# null values function
null_list <- function(x){
  map_chr(x, ~{ifelse(is.null(.x), NA, .x)})
}

is.not.null <- function(x) !is.null(x)
n <- length(johnny_followers)


# For loop for going to url of each follower and take further info

# loop for extracting each follower from github url

for (i in 1:n)
{
  # fetch data by taking one follower
  login = johnny_followers[[i]]$login
  
  # fetch the follower's profile
  f_profile <- gh("GET /users/:login", login = login, .limit = Inf)
  
  # rest of the data considered
  name = f_profile$name
  public_repos =f_profile$public_repos
  followers = f_profile$followers
  
  # null values checking an updating dataframe
  if (is.not.null(name) & is.not.null(login) & is.not.null(public_repos) 
      & is.not.null(followers))
  {
    df_johnny_followers <- rbind(df_johnny_followers, data.frame(User=null_list(name),
                                                   login = (login),
                                                   public_repos=null_list(public_repos),
                                                   followers = null_list(followers)))
  }
}
```

Visualizing the tabular data using Kable

```{r}

head(df_johnny_followers, n = 10) %>% 
  kable() %>% 
  kable_styling(bootstrap_options = c("bordered","condensed","responsive"))
```
### **Table 3**

Creating a table showing johnny chiver’ name, size, forks_count, open_issues_count, closed_issue_count.

A new column for year has been created for better visulaization.

Reository information fetching and showing the length of repository

```{r}

# repository info fetching 
johnny_repos <- gh("GET /users/johnny-chivers/repos", username = "johnny-chivers",.limit = Inf)
length(johnny_repos)

```

Dataframe creation for extracting repository information

```{r}

# dataframe creation
johnny_repos_info <- data.frame(Repo_Name=character(),
                               size=integer(), 
                               forks=integer(), 
                               open_issues_count=integer(),
                               closed_issues_count=integer()) 

# loop for getting data from each repository

for (i in 1:length(johnny_repos))
{ 
  
  # finding all required columns 
  name = johnny_repos[[i]]$name
  size = johnny_repos[[i]]$size
  created_year = as.integer(substring(johnny_repos[[i]]$created_at,1,4))
  forks = johnny_repos[[i]]$forks_count
  open_issues_count = johnny_repos[[i]]$open_issues_count
  
  closed_issues_url <-
    paste0(johnny_repos[[i]]$url,"/issues?state=closed")
  
  closed_issues = gh(closed_issues_url,username = "johnny-chivers",.limit = Inf)
  closed_issues_count = length(closed_issues)
  
  # extracting data into dataframe
  if (is.not.null(name) & is.not.null(size) & is.not.null(forks)
      & is.not.null(created_year)
      & is.not.null(open_issues_count) & is.not.null(closed_issues_count))
  {
    johnny_repos_info<-rbind(johnny_repos_info, data.frame(Repo_Name = null_list(name),
                                                         size = null_list(size),
                                                         forks = null_list(forks),
                                                         created_year = null_list(created_year),
                                                         open_issues_count = null_list(open_issues_count),
                                                         closed_issues_count = null_list(closed_issues_count)))
  }
  
}

```

Visualizing the tabular data using Kable

```{r}

head(johnny_repos_info, n = 15) %>% kable() %>%
  kable_styling(bootstrap_options = c("bordered","condensed","responsive"))

```

### **Data Visualization:**

### **1. Bar Plot of Forks vs Repository Name**

We are making use of ggplot library in the tidyverse package along with bar function and themes for showing the variation of forks created for each repository.

```{r }

# Summary creation
Johnny_popular_repos <- johnny_repos_info %>% 
  arrange(desc(forks))

df <- head(Johnny_popular_repos)

# create the plot using ggplot 
ggplot(df, 
       aes(x = Repo_Name, y = forks)) +
  geom_bar(stat = "identity", position = "dodge") + 
  theme_solarized() +
  scale_color_gdocs() +
  theme(axis.text.x=element_text(angle = 30, vjust = 0.5)) +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom") +
  ggtitle("Popular Repos ") +
  xlab("Repo Name") +
  ylab ("Number of Forks")

```

_From the above bar plot, we observe that, ElasticSearch reposioty is majorly forked followed by aws-data-engineering repository_ 


### **2. Box Plot of Skill Group Category vs Mean value of LinkedIn Members based on Country **

We are making use of ggplot library in the tidyverse package along gdocs themes for showing the variation of count of Repositories by year.

```{r }

df_repo_summary <- johnny_repos_info %>% group_by(created_year) %>% 
  summarise(Repo_Count = n())



# create the plot using ggplot 
ggplot(df_repo_summary, 
       aes(x = created_year, y = Repo_Count)) +
  geom_bar(stat = "identity", position = "dodge") + 
  theme_solarized() +
  scale_color_gdocs() +
  theme(axis.text.x=element_text(angle = 30, vjust = 0.5)) +
  theme(plot.title = element_text(hjust = 0.5), legend.position = "bottom") +
  ggtitle("Repo count by year") +
  xlab("Year") +
  ylab ("Number of Repos") 

```

_From the above bar plot, we observe that, around 20 repositories are created in year 2021 and it is the highest count_ 

### **Conclusion:**

**1. Github user Johnny-chivers has 33 repositories and 25 followers**

**2. From the visulaizations, we observed that ElasticSearch reposioty is majorly forked followed by aws-data-engineering repository **

**3. Also, around 20 repositories are created in year 2021 and it is the highest count **
